Deep Learning

### 2015-02-17 deepreview.tex
added the attention examples for caption generation

\begin{figure}
\begin{center}
  \vspace{0.2cm}
  \includegraphics[width=0.70\linewidth]{convnet-diagram}
\end{center}
\vspace{-0.6cm}
\caption{A typical convolutional network architecture}
\vspace{-0.8cm}
\label{fig:convnet}
\end{figure}

@@

The architecture of a typical ConvNet is shown in
figure~\ref{fig-convnet}.  It is structured as a series of stages. The
first few stages are composed of two types of layers: convolutional
layers and pooling layers. Units in a convolutional layer are
organized in {\em feature maps}, within which each unit is connected
to local patches in the feature maps of the previous layer through a
set of weights called a {\em filter bank}. The result of this local
weight sum is then passed through a non-linearity such as a ReLU.  All
units in a feature map share the same filter bank. Different feature
maps in a layer use different filter banks. The reason for this
architecture is twofold. First, in array data such as images, local
groups of values are often highly correlated forming distinctive local
motifs that are easily detected. Second, the local statistics of
images and other signals are invariant to location. In other word, if
a motif can appear in one part of the image, it could appear anywhere,
hence the idea of units at different locations sharing the same
weights, and detecting the same pattern in different parts of the
array.  Mathematically, the filtering operation performed by a feature
map is a {\em discrete convolution}, hence the name ConvNet.

@@

\begin{figure}[ht]
\fbox{
\begin{minipage}{\textwidth}
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\centerline{\includegraphics[width=0.49\linewidth]{Examples_im2txt_001.png}
\includegraphics[width=0.49\linewidth]{Examples_im2txt_002.png}}
\caption{Three examples of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from a test image, with the recurrent network trained to ``translate''
high-level representations of images into captions. GT stands for ``Ground Truth'' and was labeled by humans
whereas the other text is machine-generated.
Reproduced with permission from~\citet{Vinyals-et-al-arxiv2014}.
}
\label{fig:caption-generation}
\end{minipage}
}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \vspace{0.2cm}
  \includegraphics[width=0.70\linewidth]{convnet-diagram}
\end{center}
\vspace{-0.6cm}
\caption{The outputs of each layer of a typical convolutional network architecture
applied on the image of a handwritten digit (on the top left). Each rectangular
image corresponds to one of the features, detected at each of the image positions.
Each column corresponds to a layer, with information flowing from the left to
the right.
}
%\vspace{-0.8cm}
\label{fig:convnet}
\end{figure}

@@

The architecture of a typical ConvNet is shown in
figure~\ref{fig:convnet}.  It is structured as a series of stages. The
first few stages are composed of two types of layers: convolutional
layers and pooling layers. Units in a convolutional layer are
organized in {\em feature maps}, within which each unit is connected
to local patches in the feature maps of the previous layer through a
set of weights called a {\em filter bank}. The result of this local
weight sum is then passed through a non-linearity such as a ReLU.  All
units in a feature map share the same filter bank. Different feature
maps in a layer use different filter banks. The reason for this
architecture is twofold. First, in array data such as images, local
groups of values are often highly correlated forming distinctive local
motifs that are easily detected. Second, the local statistics of
images and other signals are invariant to location. In other word, if
a motif can appear in one part of the image, it could appear anywhere,
hence the idea of units at different locations sharing the same
weights, and detecting the same pattern in different parts of the
array.  Mathematically, the filtering operation performed by a feature
map is a {\em discrete convolution}, hence the name ConvNet.

@@

\begin{figure}[htp*]
\fbox{
\begin{minipage}{\textwidth}
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
%\centerline{\includegraphics[width=0.49\linewidth]{Examples_im2txt_001.png}}
%\includegraphics[width=0.49\linewidth]{Examples_im2txt_002.png}}
\centerline{\includegraphics[width=\linewidth]{good_capgen_examples.pdf}}
%\centerline{\includegraphics[width=0.49\linewidth]{Examples_im2txt_001.png}
\caption{Top: two examples of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from a test image, with the recurrent network trained to ``translate''
high-level representations of images into captions. 
Reproduced with permission from~\citet{Vinyals-et-al-arxiv2014}.
Bottom: when the RNN is given the ability to focus its attention on a different
location in the input image (lighter = more attention) as it generates each word (underlined), we
found that it exploits this to achieve better ``translation'' of images into captions.
}
\label{fig:caption-generation}
\end{minipage}
}
\end{figure}
